---
title: "Analysis_m"
author: "Suein Choi"
date: "2022-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(readxl)
library(tidyverse)
library(NonCompart)
library(plotly)
library(gtsummary)
library(kableExtra)
library(PerformanceAnalytics)
my_theme <-
  list(
    # round large p-values to two places
    "pkgwide-fn:pvalue_fun" = function(x) style_pvalue(x, digits = 2),
    "pkgwide-fn:prependpvalue_fun" = function(x) style_pvalue(x, digits = 2, prepend_p = TRUE),
    # report median (IQR) and n (percent) as default stats in `tbl_summary()`
    "tbl_summary-str:continuous_stat" = "{mean} ± {sd}",
    "tbl_summary-str:categorical_stat" = "{n} ({p}%)"
  )
set_gtsummary_theme(my_theme)


```

## Data

SNB101 from AIMS bio science 

1) Individual concentration plots
2) Mean+sd concentration plots
3) Naive NCA results
    1) After administration (time >= 0)
    2) From the beginning of administration (time >= -2)
4) Dose-normalized NCA results
    1) After administration (time >= 0)
    2) From the beginning of administration (time >= -2)
5) Simple covariate analysis using correlation & linear regression

**Plots are shown in interactive way**
Click the name (irinotecan, SN-38, SN-38G) on the label for the seperated view (Right side of the plot)


## Individual concentration plots

```{r indiv, fig.height = 12, fig.width = 10, warning = FALSE}

pkdata <- read_excel("Data/PK_NCA.xlsx")

pkdata1 <- pkdata %>%
    gather(substance, conc, 4:6) %>%
    mutate(conc = as.numeric(conc)) %>%
    filter(!is.na(conc))


ind_plot <- pkdata1 %>%
    ggplot(aes(x = time, y = conc, col = substance)) +
    geom_line(alpha = 0.3) +
    geom_point(alpha = 0.3) +
    facet_wrap(~Subject, ncol = 3, scales = "free") +
    scale_x_continuous(breaks = seq(0, 24, 4)) +
    labs(
        x = "Time (h)", y = "Plasma Concentration",
        col = " "
    ) +
    theme_bw() +
    theme(strip.background = element_rect(fill = NA, colour = NA)) +
    ggsci::scale_color_aaas()

ggplotly(ind_plot)
```


## Mean+sd concentration plot


```{r mean_sd, echo=FALSE, fig.width = 10}
mean_plot <- pkdata1 %>%
    group_by(substance, time) %>%
    mutate(mean = mean(conc), sd = sd(conc)) %>%
    ggplot(aes(x = time, y = mean, col = substance)) +
    geom_point(size = 2, alpha = 0.5) +
    geom_line(size = 0.5, alpha = 0.5) +
    geom_errorbar(aes(ymin = mean, ymax = mean + sd)) +
    facet_wrap(~substance, scales = "free_x") +
    scale_x_continuous(breaks = seq(0, 72, 24)) +
    labs(x = "Time (h)", y = "Plasma Concentration (?)") +
    theme_bw() +
    theme(strip.background = element_rect(fill = NA, colour = NA)) +
    ggsci::scale_color_aaas()


mean_plot24_both <- cowplot::plot_grid(mean_plot, mean_plot + scale_y_log10(), labels = LETTERS[1:2], ncol = 1)

mean_plot24_both

```


## Naive NCA results

NCA result with individual dose

### After end of adminitration (time >= 0)

End of administration시점부터의 NCA 계산함 (time < 0는 분석에서 제외함)

### {.tabset}

#### Irinotecan
```{r naive_nca_iri}

ncadata1 <- pkdata1 %>% filter(time >= 0) %>% as.data.frame()

ncadata2 <- pkdata1 %>% mutate(time = time+2) %>%
  arrange(Subject, substance, time) %>% as.data.frame() 

nca1 <- tblNCA(ncadata1, 
              key=c("substance", "Subject"), 
              colTime="time", 
              colConc="conc",
              R2ADJ=0.1) %>%
        select(substance, Subject, CMAX, TMAX, LAMZHL, AUCLST, AUCIFO) %>%
        as.data.frame()


kable_new <- function(data, ip){
  data %>%
        filter(substance == ip) %>%
          select(-substance) %>%
          kbl() %>%
          kable_styling(bootstrap_options = c("striped"))
}

kable_new(nca1, "irinotecan")


```

#### SN-38
```{r naive_nca_sn38}
#| collapse = TRUE
kable_new(nca1, "SN-38")

```


#### SN-38G
```{r naive_nca_sn38G}
#| collapse = TRUE

kable_new(nca1, "SN-38G")


```

#### Summary
```{r naive_nca}
#| collapse = TRUE
nca1 %>%
  select(-Subject, -TMAX) %>%
  tbl_summary(by=substance,
            digits = all_continuous() ~ 3) %>%
  modify_header(label = "**Parameter**") %>%
  bold_labels()

```


### From the beginning of administration (time >= -2)

용량 주입 시점 (time = -2) 부터의 NCA를 계산함 (Continuous infusion, duration은 2hr 로 설정)

### {.tabset}

#### Irinotecan
```{r naive_nca2_iri}


nca2 <- tblNCA(ncadata1, 
              key=c("substance", "Subject"), 
              colTime="time", 
              colConc="conc",
              R2ADJ=0.1) %>%
        select(substance, Subject, CMAX, TMAX, LAMZHL, AUCLST, AUCIFO) %>%
        as.data.frame()
kable_new(nca2, "irinotecan")


```

#### SN-38
```{r naive_nca2_sn38}
#| collapse = TRUE

kable_new(nca2, "SN-38")


```


#### SN-38G
```{r naive_nca2_sn38G}
#| collapse = TRUE
kable_new(nca2, "SN-38G")


```

#### Summary
```{r naive_nca2}
#| collapse = TRUE
nca2 %>%
  select(-Subject, -TMAX) %>%
  tbl_summary(by=substance,
            digits = all_continuous() ~ 3) %>%
  modify_header(label = "**Parameter**") %>%
  bold_labels()

```

## Dose-normalized NCA results

### After administration (time >= 0)
### {.tabset}

#### Irinotecan
```{r nca_iri}

iddose <- read_excel("Data/SNB101_Phase I_raw data_20221011 (1).xlsx", sheet="dose") 
snrn1 <- read_excel("Data/SNB101_Phase I_raw data_20221011.xlsx", sheet="PKRaw_Cycle 1")  
snrn <- t(snrn1[1:2, 2:17]) %>% as.data.frame() %>%  distinct()
colnames(snrn) <- c("Subject", "SID")
colnames(iddose) <- c("SID", "dose")
iddose1 <- iddose %>% full_join(snrn) %>% mutate(dose = as.numeric(dose))
iddose1[1, 3] <- "C1_01-001"

iddose1 <- iddose1 %>% 
    filter(Subject %in% unique(pkdata1$Subject))

nca_dn1 <- nca1 %>%
  left_join(iddose1) %>%
  select(-SID) %>%
  mutate(CMAX_dn = CMAX/dose, AUCLST_dn = AUCLST/dose, AUCIFO_dn = AUCIFO/dose) %>%
  select(-CMAX, -TMAX, -AUCLST, -AUCIFO, -LAMZHL) %>%
  select(Subject, dose, everything()) %>%
  rename(Dose = dose)

nca_dn1_s <- nca1 %>%
  left_join(iddose1) %>%
  mutate(CMAX_dn = CMAX/dose, AUCLST_dn = AUCLST/dose, AUCIFO_dn = AUCIFO/dose) %>%
  select(-CMAX, -TMAX, -AUCLST, -AUCIFO) %>%
  select(Subject, dose, everything()) %>%
  rename(Dose = dose)

kable_new(nca_dn1, "irinotecan")


```

#### SN-38
```{r nca_sn38}
#| collapse = TRUE

kable_new(nca_dn1, "SN-38")


```


#### SN-38G
```{r nca_sn38G}
#| collapse = TRUE

kable_new(nca_dn1, "SN-38G")

```

#### Summary
```{r nca}
#| collapse = TRUE
nca_dn1 %>%
  select(-Subject) %>%
  tbl_summary(by=substance,
            digits = all_continuous() ~ 3) %>%
  modify_header(label = "**Parameter**") %>%
  bold_labels()

```



### From the beginning of administration (time >= -2)
### {.tabset}

#### Irinotecan
```{r nca2_iri, message = FALSE}

nca_dn2 <- nca2 %>%
  left_join(iddose1) %>%
  select(-SID) %>%
  mutate(CMAX_dn = CMAX/dose, AUCLST_dn = AUCLST/dose, AUCIFO_dn = AUCIFO/dose) %>%
  select(-CMAX, -TMAX, -AUCLST, -AUCIFO, -LAMZHL) %>%
  select(Subject, dose, everything()) %>%
  rename(Dose = dose)

nca_dn2_s <- nca2 %>%
  left_join(iddose1) %>%
  mutate(CMAX_dn = CMAX/dose, AUCLST_dn = AUCLST/dose, AUCIFO_dn = AUCIFO/dose) %>%
  select(-CMAX, -TMAX, -AUCLST, -AUCIFO) %>%
  select(Subject, dose, everything()) %>%
  rename(Dose = dose)

kable_new(nca_dn2, "irinotecan")


```

#### SN-38
```{r nca2_sn38}
#| collapse = TRUE

kable_new(nca_dn2, "SN-38")

```


#### SN-38G
```{r nca2_sn38G}
#| collapse = TRUE
kable_new(nca_dn2, "SN-38G")

```

#### Summary
```{r nca2}
#| collapse = TRUE
nca_dn2 %>%
  select(-Subject) %>%
  tbl_summary(by=substance,
            digits = all_continuous() ~ 3) %>%
  modify_header(label = "**Parameter**") %>%
  bold_labels()

```

## Simple covariate analysis using correlation & linear regression


### Correlation plot 

```{r}
dm <- read_excel("Data/SNB101_Phase I_raw data_20221011.xlsx", sheet= "DM") %>% 
  select(1,4,5) 
hw <- read_excel("Data/SNB101_Phase I_raw data_20221011.xlsx", sheet = "HW") %>%
  select(1, 3, 6, 8)

colnames(dm) <- c("SID", "age", "sex")
colnames(hw) <- c("SID", "VISIT", "WT", "BSA")
cordata <- nca_dn1_s %>% left_join(dm) %>% left_join(hw %>% filter(VISIT == "C1D1"))
cordata_r <- cordata %>%
  mutate(sex = ifelse(sex == "남성", 1, 0)) %>%
  mutate_at(vars("age", "WT", "BSA"), as.numeric) %>%
  select(substance, LAMZHL, CMAX_dn, AUCLST_dn, AUCIFO_dn, age, sex, WT, BSA) 
chart.Correlation(cordata_r %>% filter(substance == "irinotecan") %>% select(-substance, -sex), histogram = TRUE, pch = 19)

```


### Linear regression (Univariate) result

```{r}
cordata_lm <- cordata %>%
  mutate_at(vars("age", "WT", "BSA"), as.numeric) %>%
  select(substance, LAMZHL, CMAX_dn, AUCLST_dn, AUCIFO_dn, age, sex, WT, BSA)

m1 <- lm(LAMZHL ~ sex + age + WT+ BSA, data = cordata_lm)
m2 <- lm(CMAX_dn ~ sex + age + WT+ BSA, data = cordata_lm)
m3 <- lm(AUCLST_dn ~ sex + age + WT+ BSA, data = cordata_lm)

tbl_merge(list(tbl_regression(m1),tbl_regression(m2),tbl_regression(m3)),
    tab_spanner = c("**LAMZHL**", "**CMAX_dn**", "**AUCLST_dn**"))

```

### Simple distribution for categorical variable (sex)
### {.tabset}

#### LAMZHL
```{r a}
#| collapse = TRUE

density_cor <- function(i){
cordata_lm %>%
    mutate(sex = ifelse(sex == "남성", "male", "female")) %>%
    ggplot(aes(x = {{i}}, col = sex, fill = sex)) +
    geom_density(alpha = 0.3) +
    facet_wrap(vars(substance), scale ="free")+
    theme_bw() +
    theme(strip.background = element_rect(fill = NA, colour = NA)) +
    scale_color_manual(values = c("red", "blue"), aesthetics = c("colour", "fill"))}

density_cor(LAMZHL)
```

#### CMAX_dn 
```{r b}
#| collapse = TRUE
density_cor(CMAX_dn)
```


#### AUCLST_dn 
```{r c}
#| collapse = TRUE
density_cor(AUCLST_dn)
```

